---
title: "Reproducibility Report: Baxter-King, Coppock, Straus and Vavreck (2025)"
subtitle: "Endorsements vs. Information: Experimental Evidence of Backlash and Parallel Persuasion during the COVID-19 Public Health Crisis"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: baxter-king_etal_2025_report.pdf
    toc: true
    number-sections: true
    keep-tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)
here::i_am("README.qmd")

# kableExtra styling and the vector figures are LaTeX-only; the GitHub README
# build takes plain pipe tables and the PNG copies of the figures.
latex_out <- knitr::is_latex_output()

gt <- read_csv(here("ground_truth", "baxter-king_etal_2025_ground_truth.csv"),
               show_col_types = FALSE)
coverage <- read_csv(here("ground_truth", "float_coverage.csv"), show_col_types = FALSE)
run_status <- read_csv(here("ground_truth", "archive_run_status.csv"), show_col_types = FALSE)
overwrites <- read_csv(here("ground_truth", "archive_overwrites.csv"), show_col_types = FALSE)
manifest <- read_csv(here("original_manifest.csv"), show_col_types = FALSE)
published_claims <- read_csv(here("ground_truth", "published_claims.csv"), show_col_types = FALSE)
equivalence <- read_csv(here("maintained", "output", "text_equivalence_claims.csv"),
                        show_col_types = FALSE)

n_match <- function(column, value) sum(gt[[column]] == value, na.rm = TRUE)
n_na <- function(column) sum(is.na(gt[[column]]))

status_count <- function(which_pass, which_status) {
  sum(run_status$pass == which_pass & run_status$status == which_status)
}

show_table <- function(d, caption = NULL) {
  if (latex_out) {
    kable(d, booktabs = TRUE, caption = caption) |>
      kable_styling(latex_options = c("striped", "scale_down"))
  } else {
    kable(d, caption = caption)
  }
}

figure_path <- function(stem) {
  file.path("maintained", "output",
            paste0(stem, if (latex_out) ".pdf" else ".png"))
}
```

*Drafted by Claude Opus 5 under the supervision of Alex Coppock.*

This repository holds the actively maintained replication code for Baxter-King, Coppock, Straus and Vavreck (2025), together with the reproducibility report that documents what the original archive did and did not do. It is part of a program applying the maintenance proposal in Peer, Orr and Coppock (2021, *PS: Political Science & Politics*, doi [10.1017/S1049096521000366](https://doi.org/10.1017/S1049096521000366)) to a set of published archives.

| | |
|---|---|
| Article | [10.1093/pnasnexus/pgaf185](https://doi.org/10.1093/pnasnexus/pgaf185) |
| Replication archive | [osf.io/bwv3c](https://osf.io/bwv3c/) |
| Pre-analysis plans | None; the article states the analyses were not preregistered |

**The data are not redistributed here.** The deposit lives on OSF and that is the only copy this repository points at. `download_original.R` fetches it and verifies every file; `original_manifest.csv` records the OSF file identifier, byte size, MD5 and SHA-256 of each of the `r nrow(manifest)` deposited files. OSF publishes two hashes of one set of stored bytes, computed by two different algorithms, so both are genuine checks and the script gates on both plus byte size. It also stops if `original/` holds anything the manifest does not list, and stops if a file that is already present no longer matches, which is how a mid-run write into the deposit would be caught rather than silently repaired. Re-hosting a copy would create a second archive that can drift from the first, which is the problem this project exists to document rather than to add to.

**Repository layout.** `maintained/` is the maintained rewrite: one script per published table or figure, writing to `output/`, which is committed so a reader can compare a fresh run against it without downloading anything. `ground_truth/` ties every published number to the code that produces it, and `maintained/in_text_claims.R` prints the same numbers again by an independent route. `original/` is created by the download script and is deliberately absent from the repository. This README is the reproducibility report, also available as a PDF in `report/`.

**License.** CC0 1.0 Universal, matching the terms of the deposit this repository maintains, so nothing in the chain is more restrictive than the archive itself. See `LICENSE`.

**To reproduce.** Clone or download the repository, open `baxter-king_etal_2025.Rproj`, and run:

``` r
source("run_all.R")
```

That fetches the deposited archive from OSF, verifies its checksums, fits every model, writes every table and figure into `maintained/output/`, runs the deposited code twice in a throwaway copy, rebuilds the ground truth, prints the in-text claims, and re-verifies the deposit. It takes about ten minutes. Individual scripts can be run on their own, but the three `analysis_*.R` scripts come before the tables and figures that read their model objects.

Required packages: tidyverse, estimatr, patchwork, modelsummary, knitr, kableExtra, scales, openssl, lmtest, here. Paths resolve through `here`, so nothing depends on the working directory. A successful run overwrites `maintained/output/`, which is committed: **`git diff` on that folder is the reproduction check**, and the CSV, TeX, PNG and RDS output should come back byte-identical. The five PDF figures always show as changed, because a PDF records the time it was written; compare their PNG twins instead.

## Paper Overview

**Citation**: Baxter-King, R., Coppock, A., Straus, G. and Vavreck, L. (2025). Endorsements vs. information: experimental evidence of backlash and parallel persuasion during the COVID-19 public health crisis. *PNAS Nexus*, 4(6), pgaf185.

**Research question**: Which of three kinds of persuasive appeal, endorsements, guidance and mandates, and factual information, move intentions to vaccinate and attitudes to masking, and do their effects differ by party?

**Design**: Ten survey experiments fielded in the UCLA COVID-19 Health and Politics Project between October 2020 and October 2022, among a total the article reports as 85,191 respondents. Two endorsement experiments randomize the identity of the person endorsing a vaccine; three guidance experiments randomize whether respondents are told the CDC recommends a masking policy or that vaccination is required for an activity; five information experiments randomize factual information about contagiousness and booster effectiveness. All estimates are weighted, use the Lin covariate adjustment, and take HC1 robust standard errors. Effects are reported overall and conditional on seven-point party identification.

**Main finding**: Endorsements by political figures polarize. Trump's endorsement lowered intentions to vaccinate by 9.2 points on average in October 2020 while raising them among strong Republicans, and by April 2021 endorsements by Biden and Obama lowered intentions among the still unvaccinated in both parties. Guidance and information move Democrats and Republicans in parallel: telling respondents the CDC recommended a masking policy raised support for it by 6 points with no partisan interaction, and information about the bivalent booster raised booster intentions by 8.3 points, again without partisan heterogeneity.

---

## Summary

```{r summary-numbers, include=FALSE}
rows_total <- nrow(gt)
archive_match <- n_match("match", 1)
archive_mismatch <- n_match("match", 0)
rewrite_match <- n_match("match_rewrite", 1)
rewrite_mismatch <- n_match("match_rewrite", 0)
rewrite_na <- n_na("match_rewrite")
floats_total <- nrow(coverage)
floats_covered <- sum(coverage$ground_truth_rows > 0)
```

The ground truth carries `r rows_total` rows. Where the deposited code produces a number the article prints, it reproduces it: `r archive_match` such comparisons agree at the precision the page prints and `r archive_mismatch` do not. The maintained rewrite agrees with the article on `r rewrite_match` values and disagrees on `r rewrite_mismatch`, and `r rewrite_na` rows are unverifiable because the article states no number.

### Does the deposited archive run?

The deposit ships `r nrow(overwrites)` files of code, data and metadata and no output directory. Run in order, `r status_count("as_shipped", "ok")` of its `r status_count("as_shipped", "ok") + status_count("as_shipped", "error")` scripts complete and `r status_count("as_shipped", "error")` fail. Every write in the deposit goes to a directory the deposit does not ship, so a full run overwrites `r sum(overwrites$overwritten)` of the `r nrow(overwrites)` deposited files. Running the archive in place would therefore be safe here, which is not something a reader could know without measuring it.

### Does the maintained rewrite reproduce the paper?

Yes, with one class of exception. Every coefficient, standard error, sample size and R-squared in Tables 2 and 3 and in appendix Tables S1 to S4 reproduces, as does every estimate and standard error printed on Figures 1, 3 and 5 and every number the article states in prose or in a footnote. The `r rewrite_mismatch` disagreements are the sample sizes of Table 1, which count respondents enrolled in each experiment while the deposited analysis files hold fewer rows, and one appendix claim that turns on a coding error in the deposit.

---

## Original Archive Reproducibility

### What runs, and what a stripped copy shows

The deposit is run twice in a throwaway copy, never in place. The first pass runs its scripts in the order `code/main.R` sources them and lets each see what the ones before it wrote. The second runs each script against a copy holding only deposited files, which is the test of whether a script passes only because another script left something behind.

```{r run-status}
show_table(
  run_status |>
    count(pass, status) |>
    pivot_wider(names_from = status, values_from = n, values_fill = 0) |>
    rename(Pass = pass, Errors = error, `Ran clean` = ok),
  caption = "Deposited scripts, as shipped and against a copy holding only deposited files"
)
```

```{r stripped-only, include=FALSE}
stripped_only <-
  run_status |>
  filter(status == "error") |>
  count(script) |>
  filter(n == 1) |>
  nrow()
```

`r stripped_only` scripts run in the first pass and fail in the second. All of them read a model object an earlier script wrote, which is the deposit working as intended rather than a defect: `code/main.R` sources the analysis scripts before the tables and figures. It does mean that no table or figure script in this deposit can be checked on its own.

### The two scripts that fail

```{r archive-errors}
show_table(
  run_status |>
    filter(pass == "as_shipped", status == "error") |>
    select(Script = script, Error = message),
  caption = "Deposited scripts that fail when the deposit is run in order"
)
```

`code/figures/figure_mini_meta.R`, which draws appendix Figure S62, never sources `code/helpers.R` and so cannot find the colour palette it uses. `code/figures/appendix_figures_D24_D45.R`, which draws appendix Figures S24 to S45, composes plots with `+` without loading `patchwork`; under ggplot2 4.x that is an error rather than the silent success it once was. Both are one-line fixes, and both mean that appendix figures the article cites cannot be redrawn from the deposit as it stands.

`code/figures/appendix_figures_E48_E59.R` is a third script worth naming: it exists in the deposit, the deposit's own README describes it, and `code/main.R` never sources it.

### Checksums

All `r nrow(manifest)` deposited files match the MD5, the SHA-256 and the byte size that OSF publishes for them, and `original/` holds nothing else. The manifest records those published values, so a reader can verify a fresh download against the same numbers; the report does not quote a post-run hash of any file this pipeline writes, because a PDF records the time it was written and its hash changes on every run.

---

## Errata

The maintained rewrite corrects one coding error in the deposit. It changes a claim the article makes.

**The standard error of a difference in conditional average treatment effects.** The deposit's `dic_estimator()` in `code/helpers.R` computes

``` r
std.error = sqrt(std.error_2 ^2 + std.error_2^2)
```

The second term should be `std.error_1`. As written, the Republican standard error is squared twice and the Democratic one never enters, so every standard error, p-value, confidence interval and equivalence-test p-value in the appendix's equivalence tables is computed from the wrong quantity. This is a typographical error rather than an analytical choice, so the rewrite uses `sqrt(std.error_1^2 + std.error_2^2)`.

```{r equivalence-effect, include=FALSE}
vignettes <- equivalence |> filter(family == "Mandate vignette")
affirm_corrected <- sum(vignettes$affirms_10pp)
affirm_deposited <- sum(vignettes$affirms_10pp_deposited)
```

The correction moves a published claim. The article says that among the four vaccine mandate vignettes "we can affirm equivalence at 10 points in two cases but cannot in two cases." Under the deposit's standard error `r affirm_deposited` of the four vignettes affirm equivalence at ten points; under the corrected one, `r affirm_corrected` does. The ground truth records this row as a mismatch with `defect_locus = archive`.

Two further defects in the deposit are reported rather than corrected, because correcting them would change the published figures rather than a computation.

**The series labels of Figure 2 are swapped.** `code/analysis/run_models_w3_endorse_by_arm.R` fits the models named `*_prosocial` on the subset `experiment_arm == "A (Personal)"` and the models named `*_not_prosocial` on `experiment_arm == "B (Social)"`. `code/figures/figure_2.R` then relabels `Prosocial` as `Social` and `Not Prosocial` as `Personal`. Each framing's estimates are therefore plotted under the other framing's label. The rewrite labels each series by the `experiment_arm` value the model was fitted on.

**The rows of the guidance equivalence table are swapped.** `code/tables/equiv_test_guidance.R` maps the label `G-1: CDC Mask Guidance 1` to the model object `w7_fit_cdcmask` and `G-3: CDC Mask Guidance 2` to `w6_fit_cdcmask`. G-1 is the June 2021 experiment, whose analysis file is `w6`, and G-3 is the September 2021 experiment, whose file is `w7`. The two rows of the published table carry each other's numbers.

---

## Ground Truth Verification

`ground_truth/build_ground_truth.R` runs as the last step of `run_all.R`. Every published value in it was read from the article or its appendix and is used only as a comparison target; the archive column is read from a fresh run of the deposited code and the rewrite column from `maintained/output/`, so neither can drift from the code that made it. Published values are carried as the digits the page prints, and a value agrees when the pipeline's number, printed to that precision, gives the same digits.

```{r gt-summary}
show_table(
  gt |>
    group_by(`Table or figure` = table_figure) |>
    summarize(
      Rows = n(),
      `Archive agrees` = sum(match == 1, na.rm = TRUE),
      `Rewrite agrees` = sum(match_rewrite == 1, na.rm = TRUE),
      `Rewrite differs` = sum(match_rewrite == 0, na.rm = TRUE),
      .groups = "drop"
    ) |>
    arrange(desc(Rows)),
  caption = "Ground truth by location in the article"
)
```

### Where the rewrite differs from the article

```{r gt-mismatches}
show_table(
  gt |>
    filter(match_rewrite == 0) |>
    transmute(
      Claim = claim,
      Article = value_paper,
      Rewrite = value_rewrite,
      Locus = defect_locus
    ),
  caption = "Every row where the maintained rewrite disagrees with the article"
)
```

`r sum(gt$match_rewrite == 0 & gt$table_figure == "Table 1", na.rm = TRUE)` of these are the N column of Table 1, which reports how many respondents were enrolled in each experiment. The deposited analysis file for each experiment holds fewer rows, and the deposit contains no script that assembles Table 1, so nothing in the archive can produce the published figures. One more is the headline count of respondents across the whole project: the union of the respondent identifiers in the ten deposited analysis files is larger than the 85,191 the abstract reports, so the deposit does not contain the file from which that number was counted. Another is the same gap restated in the text for E-2. The remaining `r sum(gt$match_rewrite == 0 & gt$table_figure == "Materials and methods", na.rm = TRUE)` are the equivalence claim discussed above and one appendix claim about how often the interaction terms and the differences in conditional average treatment effects agree.

### Coverage of the published floats

The float list is taken from the article and its appendix rather than from what the pipeline happens to produce: `r floats_total` floats in all, of which `r floats_covered` carry at least one ground-truth row.

```{r coverage}
show_table(
  coverage |>
    mutate(group = case_when(
      ground_truth_rows > 0 ~ "Verified cell by cell",
      str_detect(reason, "Section C") ~ "Appendix section C, per-contrast panels",
      str_detect(reason, "Section D") ~ "Appendix section D, predicted unvaccinated",
      str_detect(reason, "weighted with unweighted") ~ "Weighted against unweighted",
      str_detect(reason, "Section E") ~ "Appendix section E, vignette CATEs",
      .default = "Meta-analysis of all studies"
    )) |>
    count(`Float group` = group, name = "Floats"),
  caption = "Published floats, by whether the ground truth reaches them"
)
```

The `r floats_total - floats_covered` uncovered floats are appendix figures. None prints a number: they are two-panel plots of group means and average causal effects, in the same form as Figures 1, 3 and 5, and the coefficients behind them are the ones appendix Tables S1 to S4 print, which the ground truth verifies cell by cell. Each uncovered float carries its reason in `ground_truth/float_coverage.csv`, and the build stops if any float has neither a row nor a reason.

### Every number in the article, extracted

`ground_truth/published_claims.csv` is the exhaustive extraction: every numeric token in the article and its appendix, classified by hand.

```{r claims}
show_table(
  published_claims |>
    count(`Claim type` = claim_type, name = "Claims") |>
    arrange(desc(Claims)),
  caption = "Numeric claims in the article and appendix, by type"
)
```

A `pipeline` or `descriptive` claim must have a row in the ground truth and a block in `maintained/in_text_claims.R`; the build stops if either is missing. `definitional`, `structural` and `transcribed` claims have no pipeline counterpart by construction: a scale endpoint is checked against the survey instrument, a count of experimental groups against the pipeline object with one row per group, and a number the article takes from another source against that source.

`maintained/in_text_claims.R` prints every one of these numbers beside the article's own sentence, reaching each by its own route from the same committed output the ground truth reads. Two independent derivations that disagree have found something.

---

## Maintained Rewrite

The rewrite replaces `r n_distinct(run_status$script)` deposited scripts with `r length(list.files(here("maintained"), pattern = "[.]R$"))` files. The deposit fits each model in its own script and repeats the same forty-line block for every endorser; the rewrite fits all of them by mapping one function over a named list of arms, so a change to the specification happens in one place.

| Original | Replacement |
|---|---|
| `rm(list = ls())` | omitted |
| `setwd()` | `here::here()` with `.here` at the repository root |
| `library()` in each script | `source(here::here("maintained", "helpers.R"))` |
| `coefplot::position_dodgev()` | `position_dodge()` on the discrete y axis |
| `saveRDS()` repeated once per model | `map()` over the arms, then `walk2()` |
| Model objects saved with their environment attached | environment dropped, so two runs write identical bytes |
| `readRDS()` / `saveRDS()` | `read_rds()` / `write_rds()` |
| `%>%` | `\|>` |
| Tidy summaries saved where the table needs a fitted object | fitted objects saved throughout |

Two substitutions are worth naming. `coefplot` has not been updated since 2018 and its `position_dodgev()` is built on ggplot2 3.x internals that emit a warning for every facet under ggplot2 4.x; `position_dodge()` handles a discrete y axis natively and the panels are equivalent. And the deposit saved the mandate vignette models as tidy tables of coefficients, which is why the deposit records no sample size or R-squared for appendix Tables S3 and S4; the rewrite saves the fitted objects, so those cells have a counterpart.

The rewrite also adds four table scripts the deposit lacks or leaves incomplete: appendix Tables S1 to S4, one script each, each writing its cells unrounded to a CSV alongside the formatted LaTeX. Nothing downstream has to read a value back out of a formatted table and round it twice.

---

## Figure Verification

Figures 1, 3 and 5 print every estimate and standard error on the panel, in percentage points. All `r nrow(filter(gt, table_figure %in% c("Figure 1", "Figure 3", "Figure 5")))` of those numbers reproduce.

```{r figure-1, out.width="100%"}
knitr::include_graphics(figure_path("figure_1_trump_endorsement"))
```

```{r figure-3, out.width="100%"}
knitr::include_graphics(figure_path("figure_3_cdc_mask_guidance"))
```

```{r figure-5, out.width="100%"}
knitr::include_graphics(figure_path("figure_5_adult_booster"))
```

Figures 2 and 4 print no numbers. Each figure script writes a CSV of every estimate it plots, so the comparison is against the appendix regression tables that print the same coefficients rather than against the panel.

```{r figure-2, out.width="100%"}
knitr::include_graphics(figure_path("figure_2_all_endorsements"))
```

```{r figure-4, out.width="100%"}
knitr::include_graphics(figure_path("figure_4_mandate_vignettes"))
```

---

## Maintained Rewrite Verification

Nothing in this pipeline draws at random. There is no seed anywhere in the rewrite because there is nothing to seed: every estimate is a weighted least squares fit and every test is analytic. Running `run_all.R` twice from a clean session returns byte-identical CSV, TeX, PNG and RDS output; only the five figure PDFs differ, because a PDF records the time it was written.

The acceptance test for a full run is that `git status --porcelain maintained/output/` shows only those five PDFs.

---

## R Environment

```{r session}
show_table(
  tibble(
    Component = c("R", "tidyverse", "estimatr", "modelsummary", "ggplot2",
                  "patchwork", "kableExtra", "here"),
    Version = c(
      paste(R.version$major, R.version$minor, sep = "."),
      as.character(packageVersion("tidyverse")),
      as.character(packageVersion("estimatr")),
      as.character(packageVersion("modelsummary")),
      as.character(packageVersion("ggplot2")),
      as.character(packageVersion("patchwork")),
      as.character(packageVersion("kableExtra")),
      as.character(packageVersion("here"))
    )
  ),
  caption = "Package versions this report was built under"
)
```
